---
title: "Research"
---

<br>
As of September 2025, my research is supported by [NSERC](https://nserc-crsng.canada.ca/en) ![](../assets/img/nserc-logo){height=15}.
<br><br>

## Publications

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(bib2df)
library(dplyr)
df <- bib2df(here::here("_biblio", "papers.bib"), separate_names = TRUE)

keep_fields <- toupper(c(
  "author", "journal", "pages", "publisher", "number",
  "title", "volume", "year", "url"))

df <- df[, keep_fields] |> arrange(desc(YEAR))
source(here::here("_rcode", "render-pubs.R"))

df2 <- df |>
  transmute(
    year = clean_str(YEAR),
    title = fmt_title(TITLE, URL),
    pub = fmt_jvpy(JOURNAL, VOLUME, PAGES, YEAR, NUMBER),
    skip = is.na(URL)
  )
df2$authors = sapply(df$AUTHOR, fmt_names)
df2 <- df2 |> filter(!skip)
```

<div class="alt-url">
<ol reversed class="spaced">
```{r, error=FALSE, warning=FALSE, results="asis", echo=FALSE}
for (i in 1:nrow(df2)) {
  ref = df2[i,]
  cat('<li>\n')
  cat('<div>', ref$title, '</div>\n')
  cat('<div>', ref$authors, '</div>\n')
  cat('<div>', ref$pub, '</div>\n')
  cat('</li>\n')
}
```
</ol>
</div>

## Contributed Talks

<div class="alt-url">
<ol reversed class="spaced">
  <li>
    <b>[Upcoming] Multistate Joint Modelling of Marker and Failure Data under Dual Censoring Schemes</b>
    <br>
    ISCB Annual Conference, Freiburg, Germany<br>
    2026, September 27--October 1<br>
  </li>
  <li>
    <b>Challenges and Opportunities in the Analysis of Cervical Screening Data</b>
    <br>
    SSC Annual Meeting, Hamilton, ON, Canada<br>
    2026, May 31--June 3<br>
  </li>
  <li>
    <b>Joint Models for Marker and Failure Data
    under Dual Censoring Schemes</b>
    <!-- <a href="../assets/ENAR_slides_2026_03_17-lbumbulis.pdf" target="_blank"> -->
    <!-- <i>[slides]</i></a> -->
    <br>
    ENAR Spring Meeting, Indianapolis, IN, USA<br>
    2026, March 15--18<br>
  </li>
  <li>
    <b>Dual Censoring Schemes for Marker and Failure Time Processes$^\dagger$</b>
    <br>
    SSC Annual Meeting, Saskatoon, SK, Canada<br>
    2025, May 25--28<br>
  </li>
  <li>
    <b>Robustness and Efficiency Considerations when Testing Process Reliability with a Limit of Detection$^\ddagger$</b>
    <br>
    Waterloo Student Conference in Statistics, Actuarial Science, and Finance, Waterloo, ON, Canada<br>
    2024, October 18--19<br>
  </li>
  <li>
    <b>Testing Process Reliability under a Limit of Detection: Issues of Robustness and Efficiency</b>
    <br>
    SSC Annual Meeting, St. John's, NL, Canada<br>
    2024, June 2--5<br>
  </li>
</ol>
</div>

<small>
  $^\dagger$ <em>Received SSC Student Research Presentation Award: Biostatistics Section (see the [news release](https://uwaterloo.ca/statistics-and-actuarial-science/news/congratulations-phd-students-laura-bumbulis-and-tianyi-pan) and [list of winners](https://ssc.ca/en/publications/ssc-liaison/vol-39-3-2025-06/winners-student-research-presentation-awards-2025))</em><br>
  $^\ddagger$ <em>Received Waterloo Student Conference in Statistics, Actuarial Science, and
  Finance Presentation Award</em>
  
<br>
<table style="border: none;">
  <tr><td style="width: 60px;">ENAR:</td><td>Eastern North American Region (International Biometric Society)</td></tr>
  <tr><td>ISCB:</td><td>International Society for Clinical Biostatistics</td></tr>
  <tr><td>SSC:</td><td>Statistical Society of Canada</td></tr>
</table>
<!-- ENAR: Eastern North American Region (International Biometric Society)<br> -->
<!-- ISCB: International Society for Clinical Biostatistics<br> -->
<!-- SSC: Statistical Society of Canada -->
</small>


